Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-11-15 paper/conclusion.tex
Getting ready for submission..

Manual proofreading of connectomics segmentations is currently necessary, but it is a time consuming and error-prone task. We attempt to minimize manual labor and reduce the human bottleneck. Our classifiers can detect errors and suggest potential corrections to automatically improve segmentations, but performance can increase with guided human attention. Our approach makes it easier for both novices and experts to proofread successfully, and is significantly better than the existing baseline at this task. This helps reduces the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data. Ultimately, this moves us closer to automatic proofreading. (source/data URL omitted for review).%\url{http://rhoana.org/guidedproofreading/}.

>>>>

Manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. We attempt to minimize manual labor and reduce the human bottleneck. Our classifiers can detect errors and suggest potential corrections to automatically improve segmentations, but performance can increase with guided human attention. Our approach makes it easier for both novices and experts to proofread successfully, and is significantly better than the existing baseline at this task. This helps reduce the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data. We provide our framework and data as free and open research at (source/data URL omitted for review).%\url{http://rhoana.org/guidedproofreading/}.

### 2017-11-15 paper/introduction.tex
Getting ready for submission..

This paper makes the following contributions.
%
First, we present a CNN-based boundary classifier for split errors, plus a merge
error classifier that inverts the split error classifier. This is used to
propose merge error corrections, removing the need to manually draw the missing
edge. These classifiers perform well without much training data, which is
expensive to collect for connectomics data.
%
Second, we developed a guided proofreading approach to correcting segmentation
volumes, and an assessment scenario comparing forced-choice interaction with
automatic and oracle proofreading.
%
Third, we present the results of a quantitative user study assessing
guided proofreading. Our method is able to reduce segmentation
error faster than state-of-the-art semi-automatic tools for both novice and
expert users.
%
\CHANGED{Finally, we present the first standardized benchmark for proofreading in connectomics as an open research platform.}

Guided proofreading is applicable to all existing automatic segmentation methods that
produce a label map. As such, we believe that our approach is a promising
direction to proofread segmentations more efficiently and better tackle large
volumes of connectomics imagery.

>>>>

This paper makes the following contributions.
%
First, we present a CNN-based boundary classifier for split errors, plus a merge
error classifier that inverts the split error classifier. This proposes merge error corrections, 
which removes the need to manually draw the missing
edge. These classifiers automatically reduce error with little training data, which is expensive to collect for connectomics data.
%
Second, we develop a human-guided proofreading approach to correcting segmentation
volumes, and compare forced-choice interaction with
automatic and oracle proofreading.
%
Third, we present results of a quantitative user study assessing
guided proofreading. Our method is able to reduce segmentation
error faster than state-of-the-art semi-automatic tools for both novice and
expert users.
%
Fourth, we present the first connectomics proofreading benchmark, with image, label, and human interaction data, and evaluation code.

Guided proofreading is applicable to all existing automatic segmentation methods that produce a label map.
While we train models based on traditional CNN architectures, we propose an error correction approach with human interaction that works with many classifiers.
As such, we believe that our approach is a promising direction to proofread segmentations more efficiently and better tackle large volumes of connectomics imagery.

### 2017-11-15 paper/method.tex
Getting ready for submission..

\CHANGED{To find merge errors, we generate candidate splits within a label segment and use our split error classifier to rate them. 
%If the classifier yields a result close to 0, meaning the candidate split is actually likely to be a correct one, then we assume that the label has been merged in error and that this candidate split will fix the merge error.
If the classifier yields a result close to 0, the candidate split is likely to be correct and we have found a potential correction.}

@@

%For each segmentation label, we dilate the label by 20 pixel and generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. We perform watershed on the inverted grayscale EM image. This yields 50 candidate splits.
To generate candidate splits for each segmentation label, we create 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
%For each segmentation label, we generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. 
\CHANGED{We observed that correct splits tend to include label boundaries, and so we promote their inclusion by we dilating the label by 20 pixels. This lets the watershed algorithm `pick up' the boundary more successfully. These boundaries are then individually rated using our split error classifier (Fig.~\ref{fig:merge_error}; pseudo code in supplemental).}

@@

\paragraph{Forced choice setting.} We present a user with the choice to accept or reject a correction. All potential split errors are seen. Inspecting all merge errors is not possible for users due to the sheer amount of generated borders. Therefore, we only present merge errors that have a probability threshold higher than $1-p_t$. \CHANGED{Fig.~\ref{fig:ui} shows an example correction using the forced choice setting within our framework.}

@@

\begin{figure}[t]
\includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
\caption{\CHANGED{Example error correction within the forced choice setting.} A candidate error region is shown on the left. The user must choose between the region being a split error which needs correcting (center) or not (right). Confirming the choice advances to the next potential error.} % Hovering highlights the current selection with a blue border, and a}
\label{fig:ui}
\end{figure}

>>>>

To find merge errors, we generate candidate splits within a label segment and use our split error classifier to rate them. 
%If the classifier yields a result close to 0, meaning the candidate split is actually likely to be a correct one, then we assume that the label has been merged in error and that this candidate split will fix the merge error.
If the classifier yields a result close to 0, the candidate split is likely to be correct and we have found a potential correction.

@@

%For each segmentation label, we dilate the label by 20 pixel and generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. We perform watershed on the inverted grayscale EM image. This yields 50 candidate splits.
To generate candidate splits for each segmentation label, we create 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary.
%For each segmentation label, we generate 50 potential boundaries through the region by randomly placing watershed seed points at opposite sides of the label boundary. 
We observed that correct splits tend to include label boundaries, and so we promote their inclusion by dilating the label 20 pixels. This lets the watershed algorithm `pick up' the boundary more successfully. These boundaries are then individually rated using our split error classifier (Fig.~\ref{fig:merge_error}, pseudo code in supplemental).

@@

\paragraph{Forced choice setting.} We present a user with the choice to accept or reject a correction. All potential split errors are seen. Inspecting all merge errors is not possible for users due to the sheer amount of generated borders. Therefore, we only present merge errors that have a probability threshold higher than $1-p_t$. Fig.~\ref{fig:ui} shows an example correction using the forced choice setting within our framework.

@@

\begin{figure}[t]
\includegraphics[width=\linewidth]{gfx/user_interface_split.pdf}
\caption{Example error correction within the forced choice setting. A candidate error region is shown on the left. The user must choose between the region being a split error which needs correcting (center) or not (right). Confirming the choice advances to the next potential error.} % Hovering highlights the current selection with a blue border, and a}
\label{fig:ui}
\end{figure}

### 2017-11-15 paper/related_work.tex
James edits
Getting ready for submission..

Karimov \etal~\cite{karimov_guided_volume_editing} propose guided volume editing, which measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation. This lets expert users correct labeled computer-tomography datasets, using several interactions per correction. To correct merge errors, the authors create a large number of superpixels within a single segment and then successively group them based on dissimilarities. We were inspired by this approach, but instead we generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.~\ref{sec:methods}).

>>>>

Karimov \etal~\cite{karimov_guided_volume_editing} propose guided volume editing, which measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation. This lets expert users correct labeled computer-tomography datasets, using several interactions per correction. To correct merge errors, the authors create a large number of superpixels within a single segment and then successively group them based on dissimilarities. We were inspired by this approach, but instead we generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.~\ref{sec:methods}). Recently, Zung \etal~\cite{error_detection_framework} report the successful application of 3D multiscale convolutional neural networks for error detection and correction as a post-processing step after segmentation. Their framework is purely automatic, and could be used as input to our proposed guided method.

### 2017-11-15 paper/results.tex
Getting ready for submission..

%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings. Lower VI scores indicate less distance to the ground truth and a better segmentation. For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
Additional plots \CHANGED{and confirmatory data analysis} are available as supplemental material due to limited space.

@@

\subsection{Forced Choice User Experiment}
We performed a user study to evaluate the forced choice error correction method among novices and experts. To be comparable to Haehn~\etal's Dojo user study~\cite{haehn_dojo_2014}, participants were asked to proofread the AC4 subvolume for 30 minutes. We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation with respect to the ground truth labeling (provided in \cite{haehn_dojo_2014}). For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations. 
%\CHANGED{Our hypothesis is that VI reduction is significantly better with GP than with other tools. For this, we treat VI as a continuous variable and use analysis of variance (ANOVA) followed by parametric tests (Welch's t-test).}
\CHANGED{The initial segmentation yields a} median VI $=0.476$ ($SD=0.089$), with mean VI $=0.512$ ($SD=0.09$). Most novices and all experts were able to improve upon this score with both focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).

@@

\CHANGED{Along with our classifier code, we also present this evaluation scenario to the community as the first benchmark for proofreading in connectomics. We include representative connectomics data with ground truth labels, all participant results and demographics from the interactive experiments, our complete results from this paper, and standardized metrics for comparing different proofreading approaches. This framework will facilitate further comparisons to help make progress in connectomics (link omitted for review).}

>>>>

%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings. Lower VI scores indicate less distance to the ground truth and a better segmentation. For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
Additional plots and confirmatory data analysis are available as supplemental material due to limited space.

@@

\subsection{Forced Choice User Experiment}
We performed a user study to evaluate the forced choice error correction method among novices and experts. To be comparable to Haehn~\etal's Dojo user study~\cite{haehn_dojo_2014}, participants were asked to proofread the AC4 subvolume for 30 minutes. We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation with respect to the ground truth labeling (provided in \cite{haehn_dojo_2014}). For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations. 
%\CHANGED{Our hypothesis is that VI reduction is significantly better with GP than with other tools. For this, we treat VI as a continuous variable and use analysis of variance (ANOVA) followed by parametric tests (Welch's t-test).}
The initial segmentation yields a median VI $=0.476$ ($SD=0.089$), with mean VI $=0.512$ ($SD=0.09$). Most novices and all experts were able to improve upon this score with both focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).

@@

Along with our classifier code, we also present this evaluation scenario to the community as the first benchmark for proofreading in connectomics. We include representative connectomics data with ground truth labels, all participant results and demographics from the interactive experiments, our complete results from this paper, and standardized metrics for comparing different proofreading approaches. This framework will facilitate further comparisons to help make progress in connectomics (link omitted for review).
